---
title: "Reenforcinator Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reenforcinator Overivew}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#https://kbroman.org/pkg_primer/pages/vignettes.html#:~:text=To%20include%20an%20R%20Markdown%20document%20as%20a,vignette%20will%20be%20in%20the%20inst%2Fdoc%20folder.%20
#devtools::build_vignettes() 
```

```{r load package, echo = FALSE}
require(ReenforcinateR)
require(tidyverse)
```

## Data

The 'reinforcement' data contains 10 behaviors and 1 reinforcer where the target behavior is 'o'

```{r reinforcement data, echo = FALSE}
reinforcement
```

```{r table summary, message = FALSE}
require(janitor)
reinforcement %>% tabyl(BEH)
```

## Recounter Function 

The recounter will classify events into before or after categories based on when reinforcement occurs. 

The recounter produces two outputs. The descriptive list contains a number of descriptive statistics:

```{r recounter descriptive}
recounter(reinforcement,BEH,"o","A")$descriptive_statistics
```


The recounted data frame is a dataset which can be used in regression models and for contingency table functions (i.e., contingency_table_builders):

```{r recounted data frame}

recounter(reinforcement,BEH,"o","A")$recounted_data_frame
```
