---
title: "Reenforcinator Overview"
output:
  html_document:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Reenforcinator Overview}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#https://kbroman.org/pkg_primer/pages/vignettes.html#:~:text=To%20include%20an%20R%20Markdown%20document%20as%20a,vignette%20will%20be%20in%20the%20inst%2Fdoc%20folder.%20
#devtools::build_vignettes() 

# For the header meta data  

# https://rdrr.io/cran/summarytools/f/vignettes/rmarkdown.Rmd
```

```{r load package, echo = FALSE, message = FALSE}
require(ReenforcinateR)
require(tidyverse)
```

## Data

The 'reinforcement' data contains 10 behaviors and 1 reinforcer where the target behavior is 'o'

```{r reinforcement data, echo = FALSE}
reinforcement
```

```{r table summary, message = FALSE}
require(janitor)
reinforcement %>% tabyl(BEH)
```

## Recounter Function 

The recounter will classify events into before or after categories based on when reinforcement occurs. 

The recounter produces two outputs. The descriptive list contains a number of descriptive statistics:

```{r recounter descriptive}
recounter(reinforcement,BEH,"o","A")$descriptive_statistics
```


The recounted data frame is a dataset which can be used in regression models and for contingency table functions (i.e., contingency_table_builders):

```{r recounted data frame}
recounted_reinforcement<-recounter(reinforcement,BEH,"o","A")$recounted_data_frame
```

```{r recounted data frame tabyl}
recounted_reinforcement %>% tabyl(recount_recode_stream)
```

### Contingency table Builders

The function tables_recount_table produces two lists, a process list for computing various statistics (e.g., row wise probabilities, F tables without margins, etc.) and an output list which provides contingency tables for the frequency and probabilities. 


```{r contingency table builder reinforcement process list}
tables_recount_table(recounted_reinforcement)$process_list
```

```{r contingency table builder reinforcement output list}
tables_recount_table(recounted_reinforcement)$output_list
```

# Group-wise Detection

The reinforcinator package comes with a function for applying the recounter for each level of a grouping variable (such as participant ID or video ID). 

### Data 
I illustrate the group splitting on the reinforcement data by adding a second person to the reinforcement data 
```{r reinforcement data 2}

reinforcement2<-tidyr::tibble(
  VIDELT = rep(4,11),
  TAR = rep("JAN",11),
  BEH = c("o","x","x", #4
          "A", #4
          "o","o","x", #3
          "A", #1
          "o","o","o")
)

reinforcement3 <- rbind(reinforcement,reinforcement2)

head(reinforcement3)
tail(reinforcement3)

```


### Overall Descriptives
The overall statistics are as follows (without accounting for the reinforcement process)
```{r descriptives for reinforcement 3}
require(janitor)
reinforcement3 %>% tabyl(TAR,BEH)

```


To adress whether there is a difference before or after reinforcement we must recount the data and then compare proportions
```{r reinforcement }
reinforcement_2person<-recounter(reinforcement3, BEH, "o","A")$recounted_data_frame
tables_recount_table(reinforcement_2person)$output_list
```


### Group splitting

First we split the dataframe 
```{r splitting by groups}

group_split_reinforcement_2person<-group_splitter(reinforcement3, BEH,"o","A", group = "TAR", actor = "TAR")

group_split_reinforcement_2person

```


Now we use this for the recounted dataframe split by each actor. This produces a single recounted data frame. 

```{r recounter by groups}

recounted_group_split<-group_split_recounter(group_split_reinforcement_2person, "BEH","o","A", actor = "TAR")

recounted_group_split %>% tabyl(recount_recode_stream,GROUP)

```


#### Applying Descriptives (contingency table) on recounted split data frame

Now we can apply the descriptives on the whole dataset (which accounts for group separation when sorting sequences). 


The difference here is that instead of 4 reinforcers, this is now averaging 2 sets of 2 reinforcers
```{r recounted two person descriptives}
recounted_group_split
tables_recount_table(recounted_group_split)$output_list
```


# Thomas Data
```{r thomas data set up}
tkdata<-tidyr::tibble(
  VIDELT = rep(5,14),
  TAR = rep("TK",14),
  BEH = c("o","x","x", "x", #4
          "A", #5
          "x","x","x","x", #3
          "A", #1
          "o","o","o","x")
)

tk_data_recounted<-recounter(tkdata, BEH, "o","A")$recounted_data_frame
recounter(tkdata, BEH, "o","A")$descriptive_statistics

# still off from his old example
tables_recount_table(tk_data_recounted)$output_list
tables_recount_table(tk_data_recounted)$process_list
```


### Average Probabilities
The computation should be an average for each sub-series probability

# Cleaning Functions
The Reinforcinator comes with a deleter and combiner function


### Combiner 



### Deleter


### Testing

```{r test compare two and 1 group}
# want to see the difference between the two 

split_df_1 <- group_splitter(two_person_picture,behaviorstream = BEH, 
                             behavior = "o", consequence = "A", 
                             group = "TAR")


split_df_2 <- group_splitter2(two_person_picture,behaviorstream = BEH, 
                             behavior = "o", consequence = "A", 
                             group1 = "TAR", group2 = "VIDELT", filt = TRUE)

group_split_recounter(split_df_1,"BEH","o","A","TAR")

## having issues here ... 
#Error in if (data[n_obs, behaviorstream] == consequence) { : argument is of length zero
group_split_recounter(split_df_2,"BEH","o","A","TAR")




```
